\documentclass[10pt,a4paper]{article}


% ---------- Geometry ----------
\usepackage[margin=1.7cm]{geometry}

% ---------- Fonts ----------
\usepackage[T1]{fontenc}
\usepackage{lmodern}

% ---------- Spacing ----------
\usepackage{setspace}
\setstretch{1.05}
\setlength{\parskip}{0pt}

% ---------- Pandoc list compatibility ----------
\providecommand{\tightlist}{}

% ---------- Headings ----------
\usepackage{titlesec}
\titleformat{\section}
  {\normalsize\bfseries}
  {}
  {0pt}
  {}
\titlespacing*{\section}{0pt}{1.2em}{0.6em}

% ---------- Links ----------
\usepackage[hidelinks]{hyperref}

% ---------- Header / Footer ----------
\usepackage{fancyhdr}
\setlength{\headheight}{14pt}
\pagestyle{fancy}
\fancyhf{}

\fancyhead[L]{Curriculum Vitae}
\fancyhead[R]{Thomas I. Khan}

\fancyfoot[C]{\small thomas.khan@outlook.com \quad | \quad github.com/SMT395 \quad | \quad smt395.github.io}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% ---------- Disable numbering ----------
\setcounter{secnumdepth}{0}
\pagestyle{fancy}

% ---------- Remove rules ----------
\let\hrule\relax

% ---------- Document ----------
\begin{document}

\subsection{Languages}\label{languages}

English (C2), French (C2), German (C1)

\subsection{Education}\label{education}

\subsubsection{M.Sc. in Data Science}\label{m.sc.-in-data-science}

\textbf{Université libre de Bruxelles (ULB), Faculty of Science}
(2024-Present)

Coursework: Machine Learning, Time Series, Computational Statistics, Big
Data Algorithms.

\textbf{Selected Projects}

\begin{itemize}
\tightlist
\item
  \textbf{Bayesian Inference with Fisher Information Divergence}\\
  Master's dissertation on discretised Fisher-divergence-based
  posteriors for intractable discrete likelihoods.
\item
  \textbf{Spotify Playlist Challenge}\\
  Feature-based playlist similarity and evaluation pipeline; implemented
  and benchmarked multiple metrics.
\item
  \textbf{Neural Random Forest Replication}\\
  TensorFlow re-implementation and interpretability assessment versus
  tree ensembles.
\item
  \textbf{EMG-Based Joint Angle Prediction}\\
  Ensembling models and Domain Adversarial Neural Network on sEMG;
  ranked 2nd out of 41.
\end{itemize}

\subsubsection{M.Sc. and B.Sc. in Economics (M.Sc. Cum
Laude)}\label{m.sc.-and-b.sc.-in-economics-m.sc.-cum-laude}

\textbf{Solvay Brussels School of Economics and Management} (2014-2021)

\begin{itemize}
\tightlist
\item
  Minor: Statistics and Econometrics
\item
  Focus: Econometrics, statistics, financial modelling
\end{itemize}

\subsubsection{Baccalauréat}\label{baccalauruxe9at}

\textbf{Französisches Gymnasium zu Berlin} (2013)

\subsection{Experience}\label{experience}

\subsubsection{Machine Learning Research
Assistant}\label{machine-learning-research-assistant}

\textbf{KU Leuven, Faculty of Engineering Science (Chem and Tech)}
(2024-Present)

\begin{itemize}
\tightlist
\item
  Designed and trained YOLO-based object detection models for plastic
  item localisation in heterogeneous imaging conditions.
\item
  Developed plastic-type classification models using cropped regions of
  interest with robustness constraints.
\item
  Built an end-to-end prototype integrating detection, cropping, and
  classification packaged as modular Docker services.
\item
  Established reusable ML data infrastructure enabling scalable
  experimentation.
\end{itemize}

\subsubsection{Senior Associate, Risk and Treasury
Consulting}\label{senior-associate-risk-and-treasury-consulting}

\textbf{KPMG GmbH, Frankfurt} (03/2024--10/2024)

\begin{itemize}
\tightlist
\item
  Supported ECB on-site interest-rate-risk inspections at State Street
  Bank Germany.
\item
  Implemented ALM and interest-rate-risk frameworks including fund-term
  pricing.
\end{itemize}

\subsubsection{Supervisory Analyst, Banking
Supervision}\label{supervisory-analyst-banking-supervision}

\textbf{European Central Bank (DG-OMI)} (09/2021-09/2023)

\begin{itemize}
\tightlist
\item
  Built Python, SQL, Tableau, and GitLab pipelines automating inspection
  support and reporting.
\item
  Developed internal dashboards and analytics workflows reused across
  missions.
\item
  Implemented an NLP prototype to extract findings from supervisory
  documents.
\end{itemize}

\subsection{Technical Skills}\label{technical-skills}

\begin{itemize}
\tightlist
\item
  \textbf{ML and Data Science:} PyTorch, YOLO (Ultralytics), TensorFlow,
  scikit-learn, JAX, NumPy
\item
  \textbf{Tools and Infrastructure:} Git, Docker, Label Studio, Polars,
  DuckDB, Apache Spark, Tableau
\item
  \textbf{Cloud:} AWS S3 and IAM
\end{itemize}

\subsection{Links}\label{links}

\begin{itemize}
\tightlist
\item
  GitHub: https://github.com/SMT395
\item
  Email: thomas.khan@outlook.com
\end{itemize}

\end{document}
